RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-10-22 doc/paper.tex
Literature extesion

	 \begin{table}[!ht]
		\centering
		\scalebox{0.7}{
		\begin{tabularx}{550pt}{l  l  X}  
			Algorithm          &   Paper/year &   Short details   \\ \hline
			GP         &    \cite{koza1994genetic} (1994)    & Application of GP to SR \\ 
	        Hybrid GP  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
	        DFE        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
	        Eurequa                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
        	APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
        	FFX  & \cite{mcconaghy2011ffx} (2011)  & The Fast Function Extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning \\
             ABCP &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach \\
			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection  \\ 
	       Local optimization     & \cite{kommenda2018local} (2018)   & Constants Optimization in GP by Nonlinear Least Square \\
	       SBP-GP &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
	       BSR & \cite{jin2019bayesian} (2019) & ML--based approach; Bayesian symbolic regression  \\ 
	       DSR  & \cite{petersen2019deep} (2019) & Deep Symbolic Regression based on a RNN approach further utilizing the policy gradient search \\
	       OPERON & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS \\
	       VNP    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\
	       OccamNet & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation  based on cross-entropy matching in an EA strategy	 \\

	       AI Feynman  & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it  combines neural network fitting \\
	             GOMEA  & \cite{virgolin2021improving} (2021)    & A model-based
	       EA framework called Gene-pool optimal mixing evolutionary algorithm \\
	       ITEA & \cite{de2021interaction} (2021)   & EA based approach called the interaction-transformation EA   \\
	       SA & \cite{kantor2021simulated} (2021) &  Simulated annealing approach \\

@@

>>>>

	 \begin{table}[!ht]
		\centering
		\scalebox{0.7}{
		\begin{tabularx}{550pt}{l  l  X}  
			Algorithm          &   Paper/year &   Short details   \\ \hline
			GP         &    \cite{koza1994genetic} (1994)    & Application of GP to SR \\ 
	        Hybrid GP  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
	        DFE        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
	        APF-FE                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
        	APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
        	FFX  & \cite{mcconaghy2011ffx} (2011)  & The Fast Function Extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning \\
             ABCP &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach \\
			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection  \\ 
			MRGP & \cite{arnaldo2014multiple} (2014) & It decouples and
			linearly combines a program's subexpressions via multiple regression on the target variable  \\
	       Local optimization NLS    & \cite{kommenda2018local} (2018)   & Constants Optimization in GP by Nonlinear Least Square \\
	       FEAT & \cite{la2018learning} (2018) & Features are represented as networks of multi-type expression trees  comprised of activation functions; Differentiable features are trained via gradient descent \\
	       SBP-GP &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
	       BSR & \cite{jin2019bayesian} (2019) & ML--based approach; Bayesian symbolic regression  \\ 
	       DSR  & \cite{petersen2019deep} (2019) & Deep Symbolic Regression based on a RNN approach further utilizing the policy gradient search \\
	       OPERON & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS \\
	       VNP    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\
	       OccamNet & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation  based on cross-entropy matching in an EA strategy	 \\

	       AI-Feynman  & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it  combines neural network fitting \\
	             GOMEA  & \cite{virgolin2021improving} (2021)    & A model-based
	       EA framework called Gene-pool optimal mixing evolutionary algorithm \\
	       ITEA & \cite{de2021interaction} (2021)   & EA based approach called the interaction-transformation EA   \\
	       SA & \cite{kantor2021simulated} (2021) &  Simulated annealing approach \\

@@

Our proposed algorithm was implemented in Python version 3.x. All experiments were performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode. The maximum computation time allowed for each run was limited to 1h minutes, i.e., 3600 seconds.

The following algorithms are compared: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{AFP-FE}, \textsc{ITEA}, \textsc{AFP}, \textsc{DSR}, \textsc{Operon},  a python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{SBP-GP}, \textsc{EPLEX}, \textsc{BSR}, \textsc{FEAT}, \textsc{FFX}, \textsc{MRGP} and our \textsc{Rils}-\textsc{Rols} algorithm.
